Data Management for LSST Special Programs

### 2023-10-16 sec_intro.tex
remove cite to lse-163, fix later

The image processing and data products described in the Data Products Definitions Document
\citedsp{LSE-163} that are designed for, and will be applied to, the WFD program's observations.

>>>>

The image processing and data products described in the Data Products Definitions Document
(LSE-163) that are designed for, and will be applied to, the WFD program's observations.
